Timeliness of security updates for Android

### 2015-03-25 securityupdates.tex
Tweaks

\subsection{Critical vulnerabilities}

We compiled a list of critical vulnerabilities in Android, containing information on the discovery and publication dates, the versions affected and which versions fixed the problem.
We only looked for critical vulnerabilities such as root vulnerabilities which did not require USB debugging to exploit.
If malicious code exploits a critical vulnerability then it gains control of the device.
Some phones can be `rooted' by enabling USB debugging and using the special privileges of the ADB shell to root the device but only \daAdbEnabledPerc\ of devices have USB debugging enabled.
This is not something that applications running on the phone can exploit to break out of the app sandbox and so we do not include those vulnerabilities.
Unfortunately, many published exploits use ADB for convenience and so determining whether the use of ADB is necessary to exploit the vulnerability can be difficult.

@@

We developed and maintain an open platform for filing critical vulnerabilities in a machine readable format, the \href{http://androidvulnerabilities.org/}{AndroidVulnerabilities.org}\footnote{\textbf{Note to reviewers:} we have removed our names and affiliation from the website for this review \textbf{with the exception of the contact page. Please do not visit the contact page until the review cycle has completed.}\vspace{-4em}} (\avo) website.
We seeded it with data from the CVE database, vendor lists, reports from the literature and forums.
In addition, we have received submissions or amendments from \avoNumSubmitters\ individuals.
We collected data between \avoStartDate\ and \avoEndDate\ and so does not include any information lost before the start of that period.
\avo\ currently contains \avoNumVulnerabilities\ vulnerabilities of which \avoNumVulnAllAndroid\ affect all Android devices and \avoNumVulnSpecific\ are specific to particular devices or device manufacturers.

@@

Tracking vulnerabilities is a manual task as they are not consistently recorded in other databases such as the CVE database.
In addition, the lack of a widely acknowledged unique identifier required manual analysis to identify whether two reports referenced the same vulnerability.
Previous work has assumed ``any security issue of relevance will eventually get a CVE number assigned"~\cite{Frei2010} which is currently not the case for critical Android vulnerabilities.
For some of the vulnerabilities without CVE numbers, Google confirmed that there was no CVE number and that they did not intend to get one, instead providing an Android bug number.

@@

Establishing when a vulnerability starts to pose a threat to users is difficult.
Frei et al.~\cite{Frei2010} propose the definition of the \textbf{time of disclosure}.
This occurs when the information about the vulnerability is available to the from an accepted source.
Unfortunately before we collated this information much of it was not published by an independent source, even months or years after they had been actively used.

>>>>

\subsection{Critical vulnerabilities}
We compiled a list of critical vulnerabilities in Android, containing information on the discovery and publication dates, the versions affected and which versions fixed the problem.
We only looked for critical vulnerabilities such as root vulnerabilities which did not require USB debugging to exploit.
If malicious code exploits a critical vulnerability then it gains control of the device.
Some phones can be `rooted' by enabling USB debugging and using the special privileges of the ADB shell to root the device but only \daAdbEnabledPerc\ of devices have USB debugging enabled.
This is not something that applications running on the phone can exploit to break out of the app sandbox and so we do not include those vulnerabilities.
However there have been reports of Windows malware exploiting this vector.\footnote{\url{http://www.symantec.com/connect/blogs/windows-malware-attempts-infect-android-devices}}
Unfortunately, many published exploits use ADB for convenience and so determining whether the use of ADB is necessary to exploit the vulnerability can be difficult.

@@

We developed and maintain an open platform for filing critical vulnerabilities in a machine readable format, the \href{http://androidvulnerabilities.org/}{AndroidVulnerabilities.org}\footnote{\textbf{Note to reviewers:} we have removed our names and affiliation from the website for this review \textbf{with the exception of the contact page. Please do not visit the contact page until the review cycle has completed.}\vspace{-4em}} (\avo) website.
We seeded it with data from the CVE database, vendor lists, reports from the literature and forums.
In addition, we have received submissions or amendments from \avoNumSubmitters\ individuals.
We collected data between \avoStartDate\ and \avoEndDate\ and so it does not include any information lost before the start of that period.
\avo\ currently contains \avoNumVulnerabilities\ vulnerabilities of which \avoNumVulnAllAndroid\ affect all Android devices and \avoNumVulnSpecific\ are specific to particular devices or device manufacturers.

@@

Tracking vulnerabilities is a manual task as they are not consistently recorded in other databases such as the CVE database.
In addition, the lack of a widely acknowledged unique identifier required manual analysis to identify whether two reports referenced the same vulnerability.
Previous work has assumed ``any security issue of relevance will eventually get a CVE number assigned"~\cite{Frei2010} which is currently not the case for critical Android vulnerabilities.
For some of the vulnerabilities without CVE numbers, Google confirmed that there was no CVE number and that they did not intend to get one, instead providing an internal Android bug number.

@@

Establishing when a vulnerability starts to pose a threat to users is difficult.
Frei et al.~\cite{Frei2010} propose the definition of the \textbf{time of disclosure}.
This occurs when the information about the vulnerability is available to the from an accepted source.
Unfortunately before we collated this information much of it was not published by an accepted source, even months or years after they had been actively used.
